### 2021-03-23 README.Rmd
First creation of the mSHAP function, some documentation and other package setup

---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# mshap

<!-- badges: start -->
<!-- badges: end -->

The goal of mshap is to allow SHAP values for two-part models to be easily computed.

### 2021-03-23 R/mshap.R

@@ -1,0 +1,70 @@
+#' mSHAP
+#' 
+#' A function for calculation SHAP values of two part models
+#' 
+#' This function allows the user to input the SHAP values for two separate 
+#' models (along with the expected values), and mSHAP then outputs the SHAP
+#' values of the two model predictions multiplied together.
+#'
+#' @param shap_1 SHAP values for the data set from the first model
+#' @param shap_2 SHAP values for the data set from the second model
+#' @param ex_1 the expected value of the explainer for the first model
+#' @param ex_2 the expected value of the explainer for the second model
+#'
+#' @return a list containing the multiplied SHAP values and the expected value
+#' @export
+mshap <- function(shap_1, shap_2, ex_1, ex_2) {
+  ## Error Checking
+  # check the dimensions of the SHAP values (they need to be the same)
+  if (min(dim(shap_1) == dim(shap_2)) == FALSE) {
+    stop("`shap1` and `shap2` must have the same dimensions")
+  }
+  # Check the column types of shap_1 and shap_2
+  shap_1_class <- purrr::map_chr(shap_1, class)
+  shap_2_class <- purrr::map_chr(shap_2, class)
+  if (min(c(shap_1_class, shap_2_class) %in% c("integer", "numeric")) == FALSE) {
+    stop("`shap1` and `shap2` must be only composed of numerical values")
+  }
+  # Check the type of the input on the expected values
+  if (!is.numeric(ex_1) | !is.numeric(ex_2)) {
+    stop("`ex_1` and `ex_2` must be numeric")
+  }
+  # Check the length of the expected value inputs
+  if (length(ex_1) > 1) {
+    warning("`ex1` has a length greater than 1, only using first element")
+    ex_1 <- ex_1[1]
+  }
+  if (length(ex_2) > 1) {
+    warning("`ex2` has a length greater than 1, only using first element")
+    ex_2 <- ex_2[1]
+  }
+  
+  d <- purrr::map_dfc(
+    .x = 1:ncol(shap_1),
+    .f = ~{
+      (shap_1 %>% dplyr::pull(.x)) * c(ex_2) + 
+        (shap_2 %>% dplyr::pull(.x)) * c(ex_1) + 
+        ((shap_1 %>% dplyr::pull(.x)) * (shap_2 %>% rowSums())) / 2 +
[…]

### 2021-04-13 R/mshap.R
added observation and summary plot functions (primitive forms) and started working on a vignette

@@ -39,6 +39,19 @@ mshap <- function(shap_1, shap_2, ex_1, ex_2) {
     ex_2 <- ex_2[1]
   }
   
+  if ("matrix" %in% class(shap_1)) {
+    shap_1 <- as.data.frame(shap_1)
+  }
+  if ("matrix" %in% class(shap_2)) {
+    shap_2 <- as.data.frame(shap_2)
+  }
+  if ("array" %in% class(ex_1)) {
+    ex_1 <- c(ex_1)
+  }
+  if ("array" %in% class(ex_2)) {
+    ex_2 <- c(ex_2)
+  }
+  
   d <- purrr::map_dfc(
     .x = 1:ncol(shap_1),
     .f = ~{
@@ -48,11 +61,15 @@ mshap <- function(shap_1, shap_2, ex_1, ex_2) {
         ((shap_1 %>% rowSums()) * (shap_2 %>% dplyr::pull(.x))) / 2
     }
   ) %>%
-    magrittr::set_colnames(colnames(shap_1))
+    magrittr::set_colnames(colnames(shap_1)) %>%
+    suppressMessages()
   
-  expected_value <- d %>% 
-    rowSums() %>% 
-    mean()
+  preds_1 <- rowSums(shap_1 %>% dplyr::mutate(ex_val = ex_1))
+  preds_2 <- rowSums(shap_2 %>% dplyr::mutate(ex_val = ex_2))
+  
+  preds_3 <- preds_1 * preds_2
+  
+  expected_value <- mean(preds_3)
   
   tot_s <- rowSums(abs(d))
   shap_vals <- purrr::map_dfc(

### 2021-04-13 R/observation_plot.R

@@ -1,0 +1,100 @@
+observation_plot <- function(variable_values, shap_values, expected_value, names = NULL) {
+  if (is.null(names)) {
+    names <- colnames(variable_values)
+  }
+  predicted_value <- rowSums(shap_values) + expected_value
+  individual_shap <- shap_values %>%
+    magrittr::set_colnames(names) %>%
+    tidyr::pivot_longer(
+      names_to = "covariate",
+      values_to = "shap_val",
+      cols = colnames(.)
+    ) %>%
+    dplyr::full_join(
+      variable_values %>%
+        tidyr::pivot_longer(
+          cols = colnames(.),
+          names_to = "covariate",
+          values_to = "var_val"
+        ),
+      by = c("covariate")
+    )
+  d <- individual_shap %>%
+    dplyr::mutate(covariate = forcats::fct_reorder(covariate, shap_val, abs)) %>%
+    dplyr::arrange(desc(covariate)) %>%
+    dplyr::mutate(
+      bar_end = cumsum(shap_val) + c(expected_value),
+      bar_start = c(expected_value, head(bar_end, -1)),
+      is_positive = shap_val > 0
+    ) 
+  d %>%
+    ggplot2::ggplot() +
+    ggplot2::aes(
+      x = covariate, 
+      xmin = as.numeric(covariate) - 0.25, 
+      xmax = as.numeric(covariate) + 0.25, 
+      ymin = bar_end, 
+      ymax = bar_start, 
+      label = var_val,
+      fill = is_positive
+    ) + 
+    ggplot2::geom_hline(
+      ggplot2::aes(yintercept = expected_value),
+      color = "#849698",
+      size = 1.5
+    ) +
+    ggplot2::geom_rect(stat = "identity") +
+    ggplot2::scale_fill_manual(values = setNames(c("#A54657", "#0D3B66"), c(FALSE, TRUE))) +
+    ggplot2::coord_flip(clip = "off") +
+    ggplot2::geom_segment(
+      ggplot2::aes(
+        y = bar_end,
+        yend = bar_end,
+        x = as.numeric(covariate) + 0.25,
+        xend = as.numeric(covariate) - 1.25
+      ),
+      color = "#849698",
+      lwd = 1
+    ) +
+    ggplot2::theme_classic() +
+    ggplot2::geom_hline(
+      ggplot2::aes(yintercept = predicted_value),
+      color = "#EE964B",
+      size = 1.5
+    ) +
+    ggplot2::scale_y_continuous(
[…]

### 2021-04-13 R/summary_plot.R

@@ -1,0 +1,76 @@
+summary_plot <- function(variable_values, shap_values, names = NULL) {
+  variable_values <- variable_values %>%
+    dplyr::mutate(
+      dplyr::across(dplyr::everything(), .fns = ~((.x - min(.x)) / (max(.x) - min(.x))))
+    ) %>%
+    tidyr::pivot_longer(
+      names_to = "variable",
+      values_to = "var_val",
+      cols = colnames(.)
+    )
+  
+  if (is.null(names)) {
+    names <- colnames(variable_values)
+  }
+  
+  important_vars <- shap_values %>%
+    magrittr::set_colnames(names) %>%
+    tidyr::pivot_longer(
+      names_to = "variable",
+      values_to = "value",
+      cols = colnames(.)
+    ) %>%
+    dplyr::mutate(value = abs(value)) %>%
+    dplyr::group_by(variable) %>%
+    dplyr::summarize(avg_value = mean(value)) %>%
+    dplyr::ungroup() %>%
+    dplyr::arrange(avg_value) %>%
+    dplyr::pull(variable)
+  
+  shap_values %>%
+    magrittr::set_colnames(names) %>%
+    tidyr::pivot_longer(
+      names_to = "variable",
+      values_to = "value",
+      cols = colnames(.)
+    ) %>%
+    dplyr::bind_cols(var_val = variable_values$var_val) %>%
+    dplyr::mutate(variable = factor(variable, levels = important_vars)) %>%
+    ggplot2::ggplot() +
+    ggbeeswarm::geom_quasirandom(
+      ggplot2::aes(y = variable, x = value, color = var_val),
+      groupOnX = FALSE,
+      size = 2
+    ) + 
+    ggplot2::theme_classic() +
+    ggplot2::xlab("SHAP Value") +
+    ggplot2::ylab("Variable") +
+    ggplot2::scale_color_gradient2(
+      high = "#0D3B66",
+      mid = "#FAF0CA",
+      low = "#A54657",
+      midpoint = 0.5,
+      breaks = c(0.1, 0.9),
+      labels = c("Low", "High")
+    ) +
+    ggplot2::ggtitle("SHAP Value Summary") +
+    ggplot2::labs(color = "Value of Variable") +
+    ggplot2::theme(
+      text = ggplot2::element_text(family = "Times New Roman"),
+      legend.position = c(0.8, 0.2),
+      aspect.ratio = 0.75,
[…]

### 2021-04-15 R/mshap.R
Added a helper function for making the mshap function more robust, also finished the vignette and fixed a small bug in the summary_plot function

@@ -13,75 +13,54 @@
 #'
 #' @return a list containing the multiplied SHAP values and the expected value
 #' @export
-mshap <- function(shap_1, shap_2, ex_1, ex_2) {
-  ## Error Checking
-  # check the dimensions of the SHAP values (they need to be the same)
-  if (min(dim(shap_1) == dim(shap_2)) == FALSE) {
-    stop("`shap1` and `shap2` must have the same dimensions")
-  }
-  # Check the column types of shap_1 and shap_2
-  shap_1_class <- purrr::map_chr(shap_1, class)
-  shap_2_class <- purrr::map_chr(shap_2, class)
-  if (min(c(shap_1_class, shap_2_class) %in% c("integer", "numeric")) == FALSE) {
-    stop("`shap1` and `shap2` must be only composed of numerical values")
-  }
-  # Check the type of the input on the expected values
-  if (!is.numeric(ex_1) | !is.numeric(ex_2)) {
-    stop("`ex_1` and `ex_2` must be numeric")
-  }
-  # Check the length of the expected value inputs
-  if (length(ex_1) > 1) {
-    warning("`ex1` has a length greater than 1, only using first element")
-    ex_1 <- ex_1[1]
-  }
-  if (length(ex_2) > 1) {
-    warning("`ex2` has a length greater than 1, only using first element")
-    ex_2 <- ex_2[1]
-  }
+mshap <- function(
+  shap_1, 
+  shap_2, 
+  ex_1, 
+  ex_2,
+  shap_1_names = NULL,
+  shap_2_names = NULL
+) {
   
-  if ("matrix" %in% class(shap_1)) {
-    shap_1 <- as.data.frame(shap_1)
-  }
-  if ("matrix" %in% class(shap_2)) {
-    shap_2 <- as.data.frame(shap_2)
-  }
-  if ("array" %in% class(ex_1)) {
-    ex_1 <- c(ex_1)
-  }
-  if ("array" %in% class(ex_2)) {
-    ex_2 <- c(ex_2)
-  }
-  
-  d <- purrr::map_dfc(
-    .x = 1:ncol(shap_1),
-    .f = ~{
-      (shap_1 %>% dplyr::pull(.x)) * c(ex_2) + 
-        (shap_2 %>% dplyr::pull(.x)) * c(ex_1) + 
-        ((shap_1 %>% dplyr::pull(.x)) * (shap_2 %>% rowSums())) / 2 +
[…]

### 2021-04-15 R/multiply_shap.R

@@ -1,0 +1,104 @@
+multiply_shap <- function(
+  shap_1, 
+  shap_2, 
+  ex_1, 
+  ex_2,
+  shap_1_names = NULL,
+  shap_2_names = NULL
+) {
+  ## Error Checking
+  if ("matrix" %in% class(shap_1)) {
+    shap_1 <- as.data.frame(shap_1)
+  }
+  if ("matrix" %in% class(shap_2)) {
+    shap_2 <- as.data.frame(shap_2)
+  }
+  if (nrow(shap_1) != nrow(shap_2)) {
+    stop("`shap_1` and `shap_2` (or their elements) must have the same number of rows")
+  }
+  # check the dimensions of the SHAP values (they need to be the same)
+  if ((is.null(shap_1_names) | is.null(shap_2_names)) & (min(dim(shap_1) == dim(shap_2)) == FALSE)) {
+    stop("`shap1` and `shap2` must have the same dimensions, or you must supply `shap_1_names` and `shap_2_names`")
+  } else if (min(dim(shap_1) == dim(shap_2)) == FALSE) {
+    shap_2_missing_names <- setdiff(shap_1_names, shap_2_names)
+    shap_1_missing_names <- setdiff(shap_2_names, shap_1_names)
+    colnames(shap_1) <- shap_1_names
+    colnames(shap_2) <- shap_2_names
+    if (length(shap_2_missing_names) > 0) {
+      shap_2_missing <- matrix(0, nrow = nrow(shap_1), ncol = length(shap_2_missing_names)) %>%
+        as.data.frame() %>%
+        magrittr::set_colnames(shap_2_missing_names)
+      shap_2 <- shap_2 %>%
+        dplyr::bind_cols(shap_2_missing)
+    }
+    if (length(shap_1_missing_names > 0)) {
+      shap_1_missing <- matrix(0, nrow = nrow(shap_2), ncol = length(shap_1_missing_names)) %>%
+        as.data.frame() %>%
+        magrittr::set_colnames(shap_1_missing_names)
+      shap_1 <- shap_1 %>%
+        dplyr::bind_cols(shap_1_missing)
+    }
+    # Make sure the columns are in the same order
+    shap_2 <- shap_2 %>%
+      dplyr::select(colnames(shap_1))
+  }
+  # Check the column types of shap_1 and shap_2
[…]

### 2021-04-15 R/summary_plot.R

@@ -1,4 +1,8 @@
 summary_plot <- function(variable_values, shap_values, names = NULL) {
+  if (is.null(names)) {
+    names <- colnames(variable_values)
+  }
+  
   variable_values <- variable_values %>%
     dplyr::mutate(
       dplyr::across(dplyr::everything(), .fns = ~((.x - min(.x)) / (max(.x) - min(.x))))
@@ -8,10 +12,6 @@ summary_plot <- function(variable_values, shap_values, names = NULL) {
       values_to = "var_val",
       cols = colnames(.)
     )
-  
-  if (is.null(names)) {
-    names <- colnames(variable_values)
-  }
   
   important_vars <- shap_values %>%
     magrittr::set_colnames(names) %>%

### 2021-04-15 README.Rmd
extensive editing to the readment, documentation and update of code

@@
 )
+devtools::load_all()
+library(reticulate) # for accessing python objects from r and vice-versa
+library(insuranceData) # for the data
+library(dplyr) # for the data manipulation
+library(purrr)
+```
+
+```{python, include=FALSE}
+import numpy as np
+import pandas as pd
+import shap
+import sklearn.ensemble as sk
 ```
@@
 The goal of mshap is to allow SHAP values for two-part models to be easily computed.
+A two-part model is one where the output from one model is multiplied by the output from another model.
+These are often used in the Actuarial industry, but have other use cases as well.
+
+This package is designed in `R` with the example use cases having models and shap values calculated in python.
+It is the hope that the interoperability between the two languages continues to grow, and the example here makes a strong case for the ease of transitioning between the two.
+
+## Installation
+
+Install mSHAP from CRAN with the following code:
+```r
+install.packages("mshap")
+```
+
+Or the development version from github with:
+
+```r
+# install.packages("devtools")
+devtools::install_github("srmatth/mshap")
+```
+
+## Basic Use
+
+We will demonstrate a simple use case on simulated data.
+Suppose that we wish to be able to predict to total amount of money a consumer will spend on a subscription to a software product.
+We might simulate 4 explanatory variables that looks like the following:
+
+```{r}
+## R
+set.seed(16)
+age <- runif(1000, 18, 60)
+income <- runif(1000, 50000, 150000)
+married <- as.numeric(runif(1000, 0, 1) > 0.5)
+sex <- as.numeric(runif(1000, 0, 1) > 0.5)
+# For the sake of simplicity we will have these as numeric already, where 0 represents male and 1 represents female
+```
+
+Now because this is a contrived example, we will knowingly set the response variables as follows (suppose here that `cost_per_month` is usage based, so as to be continuous):
+
+```{r}
+## R
+cost_per_month <- (0.0006 * income - 0.2 * sex + 0.5 * married - 0.001 * age) + 10
+num_months <- (0.0001 * income + 0.0001 * sex + 0.05 * married - 0.05 * age) + 3
+```
+
+Thus, we have our data.  We will combine the covariates into a single data frame for ease of use in python.
+
+```{r}
+## R
+X <- data.frame(age, income, married, sex)
+```
+
+The end goal of this exercise is to predict the total revenue from the given customer, which mathematically will be `cost_per_month * num_months`.
+Instead of multiplying these two vectors together initially, we will instead create two models: one to predict `cost_per_month` and the other to predict `num_months`.
+We can then multiply the output of the two models together to get our predictions.
+
+We now move over to python to create our two models and predict on the training sets:
+```{python}
+## Python
+X = r.X
+y1 = r.cost_per_month
+y2 = r.num_months
+
+cpm_mod = sk.RandomForestRegressor(n_estimators = 100, max_depth = 10, max_features = 2)
+cpm_mod.fit(X, y1)
+
+nm_mod = sk.RandomForestRegressor(n_estimators = 100, max_depth = 10, max_features = 2)
+nm_mod.fit(X, y2)
+
+cpm_preds = cpm_mod.predict(X)
+nm_preds = nm_mod.predict(X)
+
+tot_rev = cpm_preds * nm_preds
+```
+
+We will now proceed to use TreeSHAP and subsequently mSHAP to explain the ultimate model predictions.
+
+```{python}
+## Python
+
+# because these are tree-based models, shap.Explainer uses TreeSHAP to calculate
+# fast, exact SHAP values for each model individually
+cpm_ex = shap.Explainer(cpm_mod)
+cpm_shap = cpm_ex.shap_values(X)
+cpm_expected_value = cpm_ex.expected_value
+
+nm_ex = shap.Explainer(nm_mod)
+nm_shap = nm_ex.shap_values(X)
+nm_expected_value = nm_ex.expected_value
+```
+
+```{r}
+## R
+final_shap <- mshap(
+  shap_1 = py$cpm_shap, 
+  shap_2 = py$nm_shap, 
+  ex_1 = py$cpm_expected_value, 
+  ex_2 = py$nm_expected_value
+)
+
+head(final_shap$shap_vals)
+
+final_shap$expected_value
+```
+
+As a check, you can see that the expected value for mSHAP is indeed the expected value of the model across the training data.
+```{r}
+## R
+mean(py$tot_rev)
+```
+
+We now have calculated the mSHAP values for the multiplied model outputs! This will allow us to explain our final model.
+
+The mSHAP package comes with additional functions that can be used to visualize SHAP values in R.
+What is show here are the default outputs, but these functions return `{ggplot2}` objects that are easily customizable.
+
+```{r, fig.width=5, fig.height=5,fig.align='center'}
+## R
+summary_plot(
+  variable_values = X,
+  shap_values = final_shap$shap_vals, 
+  names = c("age", "income", "married", "sex") # this is optional, since X has column names
+)
+```
+
+```{r, fig.width=5, fig.height=5,fig.align='center'}
+## R
+observation_plot(
+  variable_values = X[46,],
+  shap_values = final_shap$shap_vals[46,],
+  expected_value = final_shap$expected_value,
+  names = c("age", "income", "married", "sex")
+)
+```
+
+## Citations
+
+- For more information about SHAP values in general, you can visit the [SHAP github page](https://github.com/slundberg/shap)
+- If you use `{mshap}`, please cite [this article](https://google.com)

### 2021-04-15 R/mshap.R

@@ -1,18 +1,42 @@
 #' mSHAP
 #' 
-#' A function for calculation SHAP values of two part models
+#' A function for calculation SHAP values of two-part models.
 #' 
 #' This function allows the user to input the SHAP values for two separate 
 #' models (along with the expected values), and mSHAP then outputs the SHAP
 #' values of the two model predictions multiplied together.
+#' 
+#' An included feature of the function is the ability to pass data frames 
+#' that do not have the same number of columns. Say for instance that one
+#' model benefits from a certain variable but the other does not. As long
+#' as the `shap_*_names` arguments are supplied, the function will 
+#' automatically add a column of 0's for missing variables in either data frame
+#' (matrix). This corresponds to a SHAP value of 0, which of course is accurate
+#' if the variable was not included in the model.
 #'
-#' @param shap_1 SHAP values for the data set from the first model
-#' @param shap_2 SHAP values for the data set from the second model
-#' @param ex_1 the expected value of the explainer for the first model
-#' @param ex_2 the expected value of the explainer for the second model
+#' @param shap_1,shap_2 The SHAP values that will be multiplied together.  They
+#'   may be matrices or data frames, and up to one may be a list where each 
+#'   element is a matrix or data frame (this is necessary when one of the 
+#'   models is a multinomial classifier, for instance).  Each data frame or 
+#'   matrix here must have the same number of rows, and if there are different
+#'   numbers of columns, then `shap_*_names` must be specified.
+#' @param ex_1,ex_2 The expected values of the models across the training set.
+#'   If one of the arguments `shap_*` is a list, then the corresponding `ex_*`
+#'   argument must be a vector (or array) of the same length as the list.
+#' @param shap_1_names,shap_2_names The character vector containing the names 
+#'   of the columns in `shap_1` and `shap_2`, respectively.  These must be in 
+#'   the same order as the columns themselves.  If a list is passed to one of 
+#'   the `shap_*` arguments, it does NOT affect the corresponding 
+#'   `shap_*_names` argument, which will still be a single character vector.
 #'
-#' @return a list containing the multiplied SHAP values and the expected value
+#' @return A list containing the multiplied SHAP values and the expected value.
+#'   Or, in the case of a list passed as one of the `shap_*` aguments, a list 
[…]

### 2021-04-15 R/multiply_shap.R

@@ -1,3 +1,16 @@
+#' Multiply SHAP
+#' 
+#' A Helper Function for the mSHAP function
+#'
+#' @param shap_1,shap2 matrices or data frames of SHAP values to be multiplied
+#' @param ex_1,ex_2 the expected values of the models that correspond to the 
+#'   shap values
+#' @param shap_1_names,shap_2_names the names of the variables in the data 
+#'   that was passed as shap values
+#'
+#' @return a list containing a data frame of SHAP values and the expected value
+#' 
+#' @noRd
 multiply_shap <- function(
   shap_1, 
   shap_2, 

### 2021-04-15 R/observation_plot.R

@@ -1,4 +1,45 @@
+#' SHAP Observation Plot
+#' 
+#' This Function plots the given contributions for a single observation, and
+#' demonstrates how the model arrived at the prediction for the given
+#' observation.
+#' 
+#' This function allows the user to pass a sing row from a data frame of SHAP 
+#' values and variable values along with an expected model output and it 
+#' returns a ggplot object displaying a specific map of the effect of Variable 
+#' value on SHAP value. It is created with `{ggplot2}`, and the returned value 
+#' is a `{ggplot2}` object that can be modified for given themes/colors.
+#' 
+#' Please note that for the `variable_values` and `shap_values` arguments,
+#' both of which are data frames, the columns must be in the same order.
+#' This is essential in assuring that the variable values and labels are 
+#' matched to the correct shap values.
+#'
+#' @param variable_values A data frame of the  values of the variables that 
+#'   caused the given SHAP values, generally will be the same data frame or 
+#'   matrix that was passed to the model for prediction.
+#' @param shap_values A data frame of shap values, either returned by `mshap()` 
+#'   or obtained from the python `{shap}` module.
+#' @param expected_value The expected value of the SHAP explainer, either 
+#'   returned by `mshap()` or obtained from the python `{shap}` module.
+#' @param names A character vector of variable names, corresponding to the
+#'   order of the columns in both `variable_values` and `shap_values`. If
+#'   `NULL` (default), then the column names of the `variable_values` are 
+#'   taken as `names`.
+#'
+#' @return A `{ggplot2}` object
+#' @export
+#'
+#' @examples
+#' # run vignette("mshap", package = "mshap") for examples
 observation_plot <- function(variable_values, shap_values, expected_value, names = NULL) {
+  if (!("ggplot2" %in% rownames(installed.packages()))) {
+    stop("You must install the `{ggplot2}` package before running this function")
+  }
+  if (!("tidyr" %in% rownames(installed.packages()))) {
+    stop("You must install the `{tidyr}` package before running this function")
+  }
+  
   if (is.null(names)) {
     names <- colnames(variable_values)
   }

### 2021-04-15 R/summary_plot.R

@@ -1,4 +1,46 @@
+#' SHAP Summary Plot
+#' 
+#' A Function for obtaining a beeswarm plot, similar to the summary plot
+#' in the `{shap}` python package.
+#' 
+#' This function allows the user to pass a data frame of SHAP values and
+#' variable values and returns a ggplot object displaying a general summary
+#' of the effect of Variable level on SHAP value by variable.
+#' It is created with `{ggbeeswarm}`, and the returned value is a `{ggplot2}`
+#' object that can be modified for given themes/colors.
+#' 
+#' Please note that for the `variable_values` and `shap_values` arguments,
+#' both of which are data frames, the columns must be in the same order.
+#' This is essential in assuring that the variable values and labels are 
+#' matched to the correct shap values.
+#'
+#' @param variable_values A data frame of the  values of the variables that 
+#'   caused the given SHAP values, generally will be the same data frame or 
+#'   matrix that was passed to the model for prediction.
+#' @param shap_values A data frame of shap values, either returned by `mshap()` 
+#'   or obtained from the python `{shap}` module.
+#' @param names A character vector of variable names, corresponding to the
+#'   order of the columns in both `variable_values` and `shap_values`. If
+#'   `NULL` (default), then the column names of the `variable_values` are 
+#'   taken as `names`.
+#'
+#' @return A `{ggplot2}` object
+#' @export
+#'
+#' @examples
+#' # run vignette("mshap", package = "mshap") for examples
 summary_plot <- function(variable_values, shap_values, names = NULL) {
+  ## Check for packages
+  if (!("ggplot2" %in% rownames(installed.packages()))) {
+    stop("You must install the `{ggplot2}` package before running this function")
+  }
+  if (!("ggbeeswarm" %in% rownames(installed.packages()))) {
+    stop("You must install the `{ggbeeswarm}` package before running this function")
+  }
+  if (!("tidyr" %in% rownames(installed.packages()))) {
+    stop("You must install the `{tidyr}` package before running this function")
+  }
+  
   if (is.null(names)) {
     names <- colnames(variable_values)
   }

### 2021-04-16 README.Rmd
Making sure that R CMD CHECK does not have any warnings or errors

@@
   collapse = TRUE,
-  comment = "#>"
+  comment = "#>",
+  fig.path = "man/figures/README-"
 )

### 2021-04-16 R/multiply_shap.R

@@ -1,3 +1,24 @@
+globalVariables(
+  c(
+    ".",
+    "avg_value",
+    "bar_end",
+    "bar_start",
+    "covariate",
+    "desc",
+    "head",
+    "installed.packages",
+    "is_positive",
+    "setNames",
+    "shap_val",
+    "value",
+    "var_val",
+    "variable"
+  )
+)
+
+
+
 #' Multiply SHAP
 #' 
 #' A Helper Function for the mSHAP function

### 2021-04-16 README.Rmd
trying to get the vignette to work in the build

@@
 - For more information about SHAP values in general, you can visit the [SHAP github page](https://github.com/slundberg/shap)
-- If you use `{mshap}`, please cite [this article](https://google.com)
+- If you use `{mshap}`, please cite [this article](https://google.com/)

### 2021-04-17 README.Rmd
Actually got the vignettes to work this time, with the windows check too I think

--- 2021-04-16 README.Rmd
@@
 
-## Citations
+## Attribution
 
 - For more information about SHAP values in general, you can visit the [SHAP github page](https://github.com/slundberg/shap)
-- If you use `{mshap}`, please cite [this article](https://google.com)
+- If you use `{mshap}`, please cite [this article](https://www.google.com/)

### 2021-04-17 R/multiply_shap.R

@@ -17,6 +17,15 @@ globalVariables(
   )
 )
 
+# .onLoad <- function(libname, pkgname) {
+#   vig_list = tools::vignetteEngine(package = 'knitr')
+#   vweave <- vig_list[['knitr::knitr']][c('weave')][[1]]
+#   vtangle <- vig_list[['knitr::knitr']][c('tangle')][[1]]
+#   tools::vignetteEngine(pkgname, weave = vweave, tangle = vtangle,
+#                         pattern = "[.]Rmd$", package = pkgname)
+#   #register_vignette_engines(pkgname)
+# }
+
 
 
 #' Multiply SHAP

### 2021-04-17 R/summary_plot.R
Slight updates to the README, added parameters to the summary plot function to make it more robust

@@ -23,23 +23,30 @@
 #'   order of the columns in both `variable_values` and `shap_values`. If
 #'   `NULL` (default), then the column names of the `variable_values` are 
 #'   taken as `names`.
-#'
+#' @param colorscale The color scale used for the color of the plot. It should
+#'   be a character vector of length three, with the low color first, the 
+#'   middle color second, and the high color third. These can be hex color 
+#'   codes or colors recognized by `{ggplot2}`.
+#' @param legend.position The position of the legend.  See `?ggplot2::theme` 
+#'   for more information.
+#' @param font_family A character string specifying the family of the text on 
+#'   the plot. Defaults to Times New Roman.
+#' @param title A character string specifying the title of the plot.
+#' 
 #' @return A `{ggplot2}` object
 #' @export
 #'
 #' @examples
 #' # run vignette("mshap", package = "mshap") for examples
-summary_plot <- function(variable_values, shap_values, names = NULL) {
-  ## Check for packages
-  if (!("ggplot2" %in% rownames(installed.packages()))) {
-    stop("You must install the `{ggplot2}` package before running this function")
-  }
-  if (!("ggbeeswarm" %in% rownames(installed.packages()))) {
-    stop("You must install the `{ggbeeswarm}` package before running this function")
-  }
-  if (!("tidyr" %in% rownames(installed.packages()))) {
-    stop("You must install the `{tidyr}` package before running this function")
-  }
+summary_plot <- function(
+  variable_values, 
+  shap_values, 
+  names = NULL,
+  colorscale = c("#A54657", "#FAF0CA", "#0D3B66"),
+  legend.position = c(0.8, 0.2),
+  font_family = "Times New Roman",
+  title = "SHAP Value Summary"
+) {
   
   if (is.null(names)) {
     names <- colnames(variable_values)
@@ -88,18 +95,18 @@ summary_plot <- function(variable_values, shap_values, names = NULL) {
     ggplot2::xlab("SHAP Value") +
     ggplot2::ylab("Variable") +
     ggplot2::scale_color_gradient2(
-      high = "#0D3B66",
-      mid = "#FAF0CA",
-      low = "#A54657",
+      high = colorscale[1],
+      mid = colorscale[2],
+      low = colorscale[3],
       midpoint = 0.5,
       breaks = c(0.1, 0.9),
       labels = c("Low", "High")
     ) +
-    ggplot2::ggtitle("SHAP Value Summary") +
[…]

### 2021-04-18 README.Rmd
Add Travis CI to the package
Slight updates to the README, added parameters to the summary plot function to make it more robust
Added tests for all functions, fixed some small bugs in the mSHAP function.

@@
 <!-- badges: start -->
+<!--[![Travis build status](https://travis-ci.com/srmatth/mshap.svg?branch=main)](https://travis-ci.com/srmatth/mshap)-->
 <!-- badges: end -->
@@
 cost_per_month <- (0.0006 * income - 0.2 * sex + 0.5 * married - 0.001 * age) + 10
-num_months <- (0.0001 * income + 0.0001 * sex + 0.05 * married - 0.05 * age) + 3
+num_months <- 15 * (0.001 * income  * 0.001 * sex * 0.5 * married - 0.05 * age)^2
 ```
@@
 observation_plot(
-  variable_values = X[46,],
-  shap_values = final_shap$shap_vals[46,],
+  variable_values = X[23,],
+  shap_values = final_shap$shap_vals[23,],
   expected_value = final_shap$expected_value,
@@
 
+For another, more complex, use case run `vignette("mshap")`.
+For more examples and options for plotting, run `vignette("mshap_plots")`.
+
 ## Attribution

### 2021-04-18 R/mshap.R

@@ -19,7 +19,8 @@
 #'   element is a matrix or data frame (this is necessary when one of the 
 #'   models is a multinomial classifier, for instance).  Each data frame or 
 #'   matrix here must have the same number of rows, and if there are different
-#'   numbers of columns, then `shap_*_names` must be specified.
+#'   numbers of columns or the columns are not the same, then `shap_*_names` 
+#'   must be specified.
 #' @param ex_1,ex_2 The expected values of the models across the training set.
 #'   If one of the arguments `shap_*` is a list, then the corresponding `ex_*`
 #'   argument must be a vector (or array) of the same length as the list.

### 2021-04-18 R/multiply_shap.R

@@ -1,33 +1,3 @@
-globalVariables(
-  c(
-    ".",
-    "avg_value",
-    "bar_end",
-    "bar_start",
-    "covariate",
-    "desc",
-    "head",
-    "installed.packages",
-    "is_positive",
-    "setNames",
-    "shap_val",
-    "value",
-    "var_val",
-    "variable"
-  )
-)
-
-# .onLoad <- function(libname, pkgname) {
-#   vig_list = tools::vignetteEngine(package = 'knitr')
-#   vweave <- vig_list[['knitr::knitr']][c('weave')][[1]]
-#   vtangle <- vig_list[['knitr::knitr']][c('tangle')][[1]]
-#   tools::vignetteEngine(pkgname, weave = vweave, tangle = vtangle,
-#                         pattern = "[.]Rmd$", package = pkgname)
-#   #register_vignette_engines(pkgname)
-# }
-
-
-
 #' Multiply SHAP
 #' 
 #' A Helper Function for the mSHAP function
@@ -49,66 +19,14 @@ multiply_shap <- function(
   shap_1_names = NULL,
   shap_2_names = NULL
 ) {
-  ## Error Checking
-  if ("matrix" %in% class(shap_1)) {
-    shap_1 <- as.data.frame(shap_1)
-  }
-  if ("matrix" %in% class(shap_2)) {
-    shap_2 <- as.data.frame(shap_2)
-  }
-  if (nrow(shap_1) != nrow(shap_2)) {
-    stop("`shap_1` and `shap_2` (or their elements) must have the same number of rows")
-  }
-  # check the dimensions of the SHAP values (they need to be the same)
-  if ((is.null(shap_1_names) | is.null(shap_2_names)) & (min(dim(shap_1) == dim(shap_2)) == FALSE)) {
-    stop("`shap1` and `shap2` must have the same dimensions, or you must supply `shap_1_names` and `shap_2_names`")
-  } else if (min(dim(shap_1) == dim(shap_2)) == FALSE) {
-    shap_2_missing_names <- setdiff(shap_1_names, shap_2_names)
-    shap_1_missing_names <- setdiff(shap_2_names, shap_1_names)
-    colnames(shap_1) <- shap_1_names
-    colnames(shap_2) <- shap_2_names
-    if (length(shap_2_missing_names) > 0) {
-      shap_2_missing <- matrix(0, nrow = nrow(shap_1), ncol = length(shap_2_missing_names)) %>%
[…]

### 2021-04-18 R/observation_plot.R

@@ -26,19 +26,36 @@
 #'   order of the columns in both `variable_values` and `shap_values`. If
 #'   `NULL` (default), then the column names of the `variable_values` are 
 #'   taken as `names`.
+#' @param fill_colors A character vector of length 2. The first element
+#'   specifies the fill of a negative SHAP value and the second element
+#'   specifies the fill of a positive SHAP value.
+#' @param connect_color A string specifying the color of the line segment that
+#'   connects the SHAP value bars
+#' @param expected_color A string specifying the color of the line that marks
+#'   the baseline value, or the expected model output.
+#' @param predicted_color A string specifying the color of the line that marks
+#'   the value predicted by the model.
+#' @param title A string specifying the title of the plot.
+#' @param font_family A string specifying the font family, defaults to Times
+#'   New Roman.
 #'
 #' @return A `{ggplot2}` object
 #' @export
 #'
 #' @examples
 #' # run vignette("mshap", package = "mshap") for examples
-observation_plot <- function(variable_values, shap_values, expected_value, names = NULL) {
-  if (!("ggplot2" %in% rownames(installed.packages()))) {
-    stop("You must install the `{ggplot2}` package before running this function")
-  }
-  if (!("tidyr" %in% rownames(installed.packages()))) {
-    stop("You must install the `{tidyr}` package before running this function")
-  }
+observation_plot <- function(
+  variable_values, 
+  shap_values, 
+  expected_value, 
+  names = NULL,
+  fill_colors = c("#A54657", "#0D3B66"),
+  connect_color = "#849698",
+  expected_color = "#849698",
+  predicted_color = "#EE964B",
+  title = "Individual Observation Explanation",
+  font_family = "Times New Roman"
+) {
   
   if (is.null(names)) {
     names <- colnames(variable_values)
@@ -53,6 +70,7 @@ observation_plot <- function(variable_values, shap_values, expected_value, names
     ) %>%
     dplyr::full_join(
       variable_values %>%
+        magrittr::set_colnames(names) %>%
         tidyr::pivot_longer(
           cols = colnames(.),
           names_to = "covariate",
@@ -81,11 +99,12 @@ observation_plot <- function(variable_values, shap_values, expected_value, names
     ) + 
     ggplot2::geom_hline(
       ggplot2::aes(yintercept = expected_value),
[…]

### 2021-04-18 R/mshap.R
Added a plot vignette, and some additional capabilities to the plotting functions.  Added exaples to all function documentation

@@ -37,7 +37,73 @@
 #' @export
 #' 
 #' @examples 
-#' # run vignette("mshap", package = "mshap") for examples
+#' 
+#' if (interactive()) {
+# Simulate shap values
+#' shap1 <- data.frame(
+#'   age = runif(1000, -5, 5),
+#'   income = runif(1000, -5, 5),
+#'   married = runif(1000, -5, 5),
+#'   sex = runif(1000, -5, 5)
+#' )
+#' shap2 <- list(
+#'   data.frame(
+#'     age = runif(1000, -5, 5),
+#'     income = runif(1000, -5, 5),
+#'     married = runif(1000, -5, 5),
+#'     sex = runif(1000, -5, 5)
+#'   ),
+#'   data.frame(
+#'     age = runif(1000, -5, 5),
+#'     income = runif(1000, -5, 5),
+#'     married = runif(1000, -5, 5),
+#'     sex = runif(1000, -5, 5)
+#'   ),
+#'   data.frame(
+#'     age = runif(1000, -5, 5),
+#'     income = runif(1000, -5, 5),
+#'     married = runif(1000, -5, 5),
+#'     sex = runif(1000, -5, 5)
+#'   )
+#' )
+#' 
+#' ex1 <- 3
+#' ex2 <- c(4, 5, 6)
+#' 
+#' # Case where both models have a single output
+#' res1 <- mshap(
+#'   shap_1 = shap1,
+#'   shap_2 = shap2[[1]],
+#'   ex_1 = ex1,
+#'   ex_2 = ex2[1]
+#' )
+#' View(res1$shap_vals)
+#' res1$expected_value
+#' 
+#' # Case where one of your models has multiple outputs that are explained
+#' res2 <- mshap(
+#'   shap_1 = shap1,
+#'   shap_2 = shap2,
+#'   ex_1 = ex1,
+#'   ex_2 = ex2
+#' )
+#' View(res2[[1]]$shap_vals)
+#' res2[[1]]$expected_value
+#' 
+#' # Case where the models have different variables
+#' res3 <- mshap(
+#'   shap_1 = shap1,
+#'   shap_2 = shap2,
+#'   ex_1 = ex1,
+#'   ex_2 = ex2,
+#'   shap_1_names = c("Age", "Income", "Married", "Sex"),
+#'   shap_2_names = c("Age", "Income", "Children", "American")
+#' )
[…]

### 2021-04-18 R/multiply_shap.R

@@ -1,4 +1,5 @@
-#' Multiply SHAP
+
+#' @title Multiply SHAP
 #' 
 #' A Helper Function for the mSHAP function
 #'
@@ -65,7 +66,7 @@ multiply_shap <- function(
 }
 
 
-#' Validate the SHAP values passed to the function
+#' @title Validate the SHAP values passed to the function
 #' 
 #' A Simple function that throws errors when certain conditions are not met for
 #' The SHAP values passed to the mSHAP function.
@@ -162,8 +163,8 @@ validate_shap <- function(
 }
 
 
-#' Global Variable Bindings so I can use unquoted variables without 
-#' package check warnings
+# Global Variable Bindings so I can use unquoted variables without 
+# package check warnings
 globalVariables(
   c(
     ".",

### 2021-04-18 R/observation_plot.R

@@ -43,7 +43,85 @@
 #' @export
 #'
 #' @examples
-#' # run vignette("mshap", package = "mshap") for examples
+#' 
+#' if (interactive()) {
+#' library(mshap)
+#' library(ggplot2)
+#' 
+#' # Generate fake data
+#' set.seed(18)
+#' dat <- data.frame(
+#'   age = runif(1000, min = 0, max = 20),
+#'   prop_domestic = runif(1000),
+#'   model = sample(c(0, 1), 1000, replace = TRUE),
+#'   maintain = rexp(1000, .01) + 200
+#' )
+#' shap <- data.frame(
+#'   age = rexp(1000, 1/dat$age) * (-1)^(rbinom(1000, 1, dat$prop_domestic)),
+#'   prop_domestic = -200 * rnorm(100, dat$prop_domestic, 0.02) + 100,
+#'   model = ifelse(dat$model == 0, rnorm(1000, -50, 30), rnorm(1000, 50, 30)),
+#'   maintain = (rnorm(1000, dat$maintain, 100) - 400) * 0.2
+#' )
+#' expected_value <- 1000
+#' 
+#' # A Basic sumary plot
+#' summary_plot(
+#'   variable_values = dat,
+#'   shap_values = shap
+#' )
+#' 
+#' # A Customized summary plot
+#' summary_plot(
+#'   variable_values = dat,
+#'   shap_values = shap,
+#'   legend.position = "bottom",
+#'   names = c("Age", "% Domestic", "Model", "Maintenence Hours"),
+#'   colorscale = c("blue", "purple", "red"),
+#'   font_family = "Arial",
+#'   title = "A Custom Title"
+#' )
+#' 
+#' # A basic observation plot
+#' observation_plot(
+#'   variable_values = dat[1,],
+#'   shap_values = shap[1,],
+#'   expected_value = expected_value
+#' )
+#' 
+#' # A Customized Observation plot
+#' observation_plot(
+#'   variable_values = dat[1,],
+#'   shap_values = shap[1,],
+#'   expected_value = expected_value,
+#'   names = c("Age", "% Domestic", "Model", "Maintenence Hours"),
+#'   font_family = "Arial",
+#'   title = "A Custom Title",
+#'   fill_colors = c("red", "blue"),
+#'   connect_color = "black",
+#'   expected_color = "purple",
+#'   predicted_color = "yellow"
+#' )
+#' 
+#' # Add elements to the returned object
[…]

### 2021-04-18 R/summary_plot.R

@@ -37,7 +37,85 @@
 #' @export
 #'
 #' @examples
-#' # run vignette("mshap", package = "mshap") for examples
+#' 
+#' if (interactive()) {
+#' library(mshap)
+#' library(ggplot2)
+#' 
+#' # Generate fake data
+#' set.seed(18)
+#' dat <- data.frame(
+#'   age = runif(1000, min = 0, max = 20),
+#'   prop_domestic = runif(1000),
+#'   model = sample(c(0, 1), 1000, replace = TRUE),
+#'   maintain = rexp(1000, .01) + 200
+#' )
+#' shap <- data.frame(
+#'   age = rexp(1000, 1/dat$age) * (-1)^(rbinom(1000, 1, dat$prop_domestic)),
+#'   prop_domestic = -200 * rnorm(100, dat$prop_domestic, 0.02) + 100,
+#'   model = ifelse(dat$model == 0, rnorm(1000, -50, 30), rnorm(1000, 50, 30)),
+#'   maintain = (rnorm(1000, dat$maintain, 100) - 400) * 0.2
+#' )
+#' expected_value <- 1000
+#' 
+#' # A Basic sumary plot
+#' summary_plot(
+#'   variable_values = dat,
+#'   shap_values = shap
+#' )
+#' 
+#' # A Customized summary plot
+#' summary_plot(
+#'   variable_values = dat,
+#'   shap_values = shap,
+#'   legend.position = "bottom",
+#'   names = c("Age", "% Domestic", "Model", "Maintenence Hours"),
+#'   colorscale = c("blue", "purple", "red"),
+#'   font_family = "Arial",
+#'   title = "A Custom Title"
+#' )
+#' 
+#' # A basic observation plot
+#' observation_plot(
+#'   variable_values = dat[1,],
+#'   shap_values = shap[1,],
+#'   expected_value = expected_value
+#' )
+#' 
+#' # A Customized Observation plot
+#' observation_plot(
+#'   variable_values = dat[1,],
+#'   shap_values = shap[1,],
+#'   expected_value = expected_value,
+#'   names = c("Age", "% Domestic", "Model", "Maintenence Hours"),
+#'   font_family = "Arial",
+#'   title = "A Custom Title",
+#'   fill_colors = c("red", "blue"),
+#'   connect_color = "black",
+#'   expected_color = "purple",
+#'   predicted_color = "yellow"
+#' )
+#' 
+#' # Add elements to the returned object
[…]

### 2021-04-19 R/observation_plot.R
update the observation plot to use the `where` function in `dplyr::across()`

@@ -149,16 +149,16 @@ observation_plot <- function(
     dplyr::full_join(
       variable_values %>%
         magrittr::set_colnames(names) %>%
-        dplyr::mutate_if(
-          is.numeric,
-          ~as.character(signif(.x, 3))
-        ) %>%
-        # dplyr::mutate(
-        #   dplyr::across(
-        #     .cols = tidyselect::where(is.numeric),
-        #     .fns = ~as.character(signif(.x, 3))
-        #   )
+        # dplyr::mutate_if(
+        #   is.numeric,
+        #   ~as.character(signif(.x, 3))
         # ) %>%
+        dplyr::mutate(
+          dplyr::across(
+            .cols = where(is.numeric),
+            .fns = ~as.character(signif(.x, 3))
+          )
+        ) %>%
         tidyr::pivot_longer(
           cols = colnames(.),
           names_to = "covariate",
@@ -246,3 +246,5 @@ observation_plot <- function(
       plot.subtitle = ggplot2::element_text(hjust = 0.5)
     )
 }
+
+utils::globalVariables("where")

### 2021-04-19 R/observation_plot.R
fixed strange warning message that was coming from the observation plot

@@ -211,17 +211,23 @@ observation_plot <- function(
       size = 1.5
     ) +
     ggplot2::scale_y_continuous(
-      breaks = expected_value,
-      labels = stringr::str_c(
-        "Baseline:\n", 
-        signif(expected_value, 6)
+      breaks = c(expected_value, predicted_value),
+      labels = c(
+        stringr::str_c(
+          "Baseline:\n", 
+          signif(expected_value, 6)
+        ),
+        ""
       ),
       sec.axis = ggplot2::sec_axis(
         trans = ~.,
-        breaks = c(predicted_value),
-        labels = stringr::str_c(
-          "Model Prediction:\n", 
-          signif(predicted_value, 6)
+        breaks = c(predicted_value, expected_value),
+        labels = c(
+          stringr::str_c(
+            "Model Prediction:\n", 
+            signif(predicted_value, 6)
+          ),
+          ""
         )
       )
     ) +
@@ -243,7 +249,8 @@ observation_plot <- function(
       ),
       axis.title = ggplot2::element_blank(),
       plot.title = ggplot2::element_text(hjust = 0.5),
-      plot.subtitle = ggplot2::element_text(hjust = 0.5)
+      plot.subtitle = ggplot2::element_text(hjust = 0.5),
+      axis.ticks.x = ggplot2::element_blank()
     )
 }
 

### 2021-04-19 README.Rmd
added badge back to readme

@@
 <!-- badges: start -->
-<!--[![Travis build status](https://travis-ci.com/srmatth/mshap.svg?branch=main)](https://travis-ci.com/srmatth/mshap)-->
+[![Travis build status](https://travis-ci.com/srmatth/mshap.svg?branch=main)](https://travis-ci.com/srmatth/mshap)
 <!-- badges: end -->

### 2021-04-24 README.Rmd
got the badge to work in the readme

@@
 <!-- badges: start -->
-[![Travis build status](https://travis-ci.com/srmatth/mshap.svg?branch=main)](https://travis-ci.com/srmatth/mshap)
+[![Travis build status](https://travis-ci.com/srmatth/mshap.svg?token=zA4xhwrbzL7YLqiktuAB&branch=main)](https://travis-ci.com/srmatth/mshap)
 <!-- badges: end -->

### 2021-05-19 README.Rmd
additional files dealing with the paper and the final model, slight updates to the plotting functions (added a num_vars argument for limiting the number of variables to 10 by default)

--- 2021-04-19 README.Rmd
@@
 <!-- badges: start -->
-[![Travis build status](https://travis-ci.com/srmatth/mshap.svg?branch=main)](https://travis-ci.com/srmatth/mshap)
+[![Travis build status](https://travis-ci.com/srmatth/mshap.svg?token=zA4xhwrbzL7YLqiktuAB&branch=main)](https://travis-ci.com/srmatth/mshap)
+[![Codecov test coverage](https://codecov.io/gh/srmatth/mshap/branch/main/graph/badge.svg)](https://codecov.io/gh/srmatth/mshap?branch=main)
 <!-- badges: end -->

### 2021-05-19 R/helpers-where.R

@@ -1,0 +1,75 @@
+#' Select variables with a function
+#'
+#' This [selection helper][language] selects the variables for which a
+#' function returns `TRUE`.
+#'
+#' @param fn A function that returns `TRUE` or `FALSE` (technically, a
+#'   _predicate_ function). Can also be a purrr-like formula.
+#'
+#' @section Examples:
+#'
+#' ```{r, child = "man/rmd/setup.Rmd"}
+#' ```
+#'
+#' Selection helpers can be used in functions like `dplyr::select()`
+#' or `tidyr::pivot_longer()`. Let's first attach the tidyverse:
+#'
+#' ```{r, comment = "#>", collapse = TRUE}
+#' library(tidyverse)
+#'
+#' # For better printing
+#' iris <- as_tibble(iris)
+#' ```
+#'
+#' `where()` takes a function and returns all variables for which the
+#' function returns `TRUE`:
+#'
+#' ```{r, comment = "#>", collapse = TRUE}
+#' is.factor(iris[[4]])
+#'
+#' is.factor(iris[[5]])
+#'
+#' iris %>% select(where(is.factor))
+#'
+#' is.numeric(iris[[4]])
+#'
+#' is.numeric(iris[[5]])
+#'
+#' iris %>% select(where(is.numeric))
+#' ```
+#'
+#'
+#' ## The formula shorthand
+#'
+#' You can use purrr-like formulas as a shortcut for creating a
+#' function on the spot. These expressions are equivalent:
+#'
+#' ```{r, comment = "#>", collapse = TRUE}
+#' iris %>% select(where(is.numeric))
+#'
+#' iris %>% select(where(function(x) is.numeric(x)))
+#'
+#' iris %>% select(where(~ is.numeric(.x)))
+#' ```
+#'
+#' The shorthand is useful for adding logic inline. Here we select all
+#' numeric variables whose mean is greater than 3.5:
+#'
+#' ```{r, comment = "#>", collapse = TRUE}
+#' iris %>% select(where(~ is.numeric(.x) && mean(.x) > 3.5))
+#' ```
+#'
+#' @name where
+where <- function(fn) {
+  predicate <- rlang::as_function(fn)
+  
+  function(x, ...) {
+    out <- predicate(x, ...)
+    
+    if (!rlang::is_bool(out)) {
+      abort("`where()` must be used with functions that return `TRUE` or `FALSE`.")
+    }
+    
+    out
+  }
+}

### 2021-05-19 R/observation_plot.R

@@ -26,6 +26,8 @@
 #'   order of the columns in both `variable_values` and `shap_values`. If
 #'   `NULL` (default), then the column names of the `variable_values` are 
 #'   taken as `names`.
+#' @param num_vars An integer specifying the number of variables to show in the
+#'   plot, defaults to the 10 most important.
 #' @param fill_colors A character vector of length 2. The first element
 #'   specifies the fill of a negative SHAP value and the second element
 #'   specifies the fill of a positive SHAP value.
@@ -127,6 +129,7 @@ observation_plot <- function(
   shap_values, 
   expected_value, 
   names = NULL,
+  num_vars = 10,
   fill_colors = c("#A54657", "#0D3B66"),
   connect_color = "#849698",
   expected_color = "#849698",
@@ -166,6 +169,21 @@ observation_plot <- function(
         ),
       by = c("covariate")
     )
+  if (nrow(individual_shap) > num_vars) {
+  to_keep <- individual_shap %>%
+    dplyr::arrange(desc(abs(shap_val))) %>%
+    dplyr::pull(covariate) %>%
+    `[`(1:num_vars)
+  individual_shap <- individual_shap %>%
+    dplyr::mutate(covariate = forcats::fct_other(covariate, keep = to_keep)) %>%
+    dplyr::group_by(covariate) %>%
+    dplyr::summarize(
+      shap_val = sum(shap_val),
+      var_val = stringr::str_c(unique(var_val), collapse = "|")
+    ) %>%
+    dplyr::ungroup()
+  }
+  
   d <- individual_shap %>%
     dplyr::mutate(covariate = forcats::fct_reorder(covariate, shap_val, abs)) %>%
     dplyr::arrange(desc(covariate)) %>%
@@ -232,7 +250,7 @@ observation_plot <- function(
       )
     ) +
     ggplot2::scale_x_discrete(
-      labels = rev(stringr::str_c(d$covariate, "\n", d$var_val))
+      labels = rev(stringr::str_c(d$covariate, "\n", ifelse(d$covariate == "Other", " ", d$var_val)))
     ) +
     ggplot2::ggtitle(title) +
     ggplot2::theme(

### 2021-05-19 R/summary_plot.R

@@ -23,6 +23,8 @@
 #'   order of the columns in both `variable_values` and `shap_values`. If
 #'   `NULL` (default), then the column names of the `variable_values` are 
 #'   taken as `names`.
+#' @param num_vars An integer specifying the number of variables to show in the
+#'   plot, defaults to the 10 most important.
 #' @param colorscale The color scale used for the color of the plot. It should
 #'   be a character vector of length three, with the low color first, the 
 #'   middle color second, and the high color third. These can be hex color 
@@ -120,6 +122,7 @@ summary_plot <- function(
   variable_values, 
   shap_values, 
   names = NULL,
+  num_vars = 10,
   colorscale = c("#A54657", "#FAF0CA", "#0D3B66"),
   legend.position = c(0.8, 0.2),
   font_family = "Times New Roman",
@@ -129,16 +132,6 @@ summary_plot <- function(
   if (is.null(names)) {
     names <- colnames(variable_values)
   }
-  
-  variable_values <- variable_values %>%
-    dplyr::mutate(
-      dplyr::across(dplyr::everything(), .fns = ~((.x - min(.x)) / (max(.x) - min(.x))))
-    ) %>%
-    tidyr::pivot_longer(
-      names_to = "variable",
-      values_to = "var_val",
-      cols = colnames(.)
-    )
   
   important_vars <- shap_values %>%
     magrittr::set_colnames(names) %>%
@@ -153,9 +146,34 @@ summary_plot <- function(
     dplyr::ungroup() %>%
     dplyr::arrange(avg_value) %>%
     dplyr::pull(variable)
+  if (length(important_vars) > num_vars) {
+    n <- length(important_vars)
+    important_vars <- important_vars[(n - num_vars + 1):n]
+  }
+  
+  variable_values <- variable_values %>%
+    dplyr::select(dplyr::all_of(important_vars)) %>%
+    dplyr::mutate(
+      dplyr::across(
+        where(is.character),
+        .fns = ~as.numeric(as.factor(.x))
+      )
+    ) %>%
+    dplyr::mutate(
+      dplyr::across(
+        dplyr::everything(), 
+        .fns = ~((.x - min(.x)) / (max(.x) - min(.x)))
+      )
+    ) %>%
+    tidyr::pivot_longer(
+      names_to = "variable",
+      values_to = "var_val",
+      cols = colnames(.)
+    )
   
   shap_values %>%
     magrittr::set_colnames(names) %>%
[…]

### 2021-05-19 inst/paper/04_get_final_model.py

@@ -1,0 +1,119 @@
+# Training of the best models for the PD data
+import logging
+import numpy as np
+import pandas as pd
+import sklearn.ensemble as sk
+import shap
+from sklearn.preprocessing import OrdinalEncoder
+
+logging.basicConfig(format='%(asctime)s - %(message)s', level=logging.INFO, filename="06_out.log")
+logging.info("libraries imported!")
+
+train = pd.read_csv("data/pd_train.csv", low_memory=False)
+train = train.dropna(axis=0)
+test = pd.read_csv("data/pd_test.csv", low_memory=False)
+test = test.dropna(axis=0)
+test = test.sample(n = 50000)
+logging.info("train and test data read in")
+
+#### Frequency Model ----
+
+X = train.drop(columns=["ULTIMATE_CLAIM_COUNT", "severity", "log_severity", "ULTIMATE_AMOUNT", "form", "X_VAR46", "X_VAR2", "X_VAR19", "X_VAR34", "EARNED_EXPOSURE"])
+y1 = train[["ULTIMATE_CLAIM_COUNT"]].values.squeeze()
+wt = train[["EARNED_EXPOSURE"]].values.squeeze()
+logging.info("train data split into predictors and response for freq mod")
+
+logging.info("creating encoding")
+enc = OrdinalEncoder(handle_unknown = "use_encoded_value", unknown_value = -1)
+logging.info("fitting encoding")
+enc.fit(X)
+logging.info("encoding the training data")
+X = enc.transform(X)
+logging.info("training data encoding created")
+
+logging.info("setting tuning parameters for model")
+freq_mod = sk.RandomForestClassifier(n_estimators = 100, max_depth = 20, max_features = 20, min_impurity_decrease = .001, max_samples = 0.632, n_jobs = -1)
+logging.info("fitting frequency model")
+freq_mod.fit(X = X, y = y1, sample_weight = wt)
+logging.info("frequency model fit")
+
+logging.info("dropping columns in the test data")
+X_test = test.drop(columns=["ULTIMATE_CLAIM_COUNT", "severity", "log_severity", "ULTIMATE_AMOUNT", "form", "X_VAR46", "X_VAR2", "X_VAR19", "X_VAR34", "EARNED_EXPOSURE"])
+logging.info("saving the test data")
+X_test.to_csv("output/pd_final_mod_test_data.csv")
+logging.info("encoding the test data")
+X_test = enc.transform(X_test)
[…]

### 2021-05-19 inst/paper/04a_visualize_final_model.R

@@ -1,0 +1,118 @@
+## Script to create visualizations of final model
+
+## Set the path to the data
+dat_dir <- "inst/paper/pd_final/"
+
+## load the mshap library
+devtools::load_all() # for development
+# library(mshap) # for when mshap is installed
+
+## Load libraries
+library(dplyr)
+library(stringr)
+library(readr)
+library(fs)
+library(purrr)
+library(magrittr)
+library(tidyr)
+library(ggplot2)
+
+## Read in the data we want
+test <- read_csv(str_c(dat_dir, "pd_final_mod_test_data.csv")) %>%
+  select(-X1) # this is the row number that came from saving the data in python
+freq_preds <- read_csv(str_c(dat_dir, "pd_freq_preds_final_mod.csv")) %>%
+  select(-X1)
+sev_preds <- read_csv(str_c(dat_dir, "pd_sev_preds_final_mod.csv")) %>%
+  select(-X1)
+
+## Create some basic plots regarding the predictions
+freq_preds %>%
+  pivot_longer(
+    cols = everything(),
+    names_to = "num_claims",
+    values_to = "prediction"
+  ) %>%
+  mutate(
+    num_claims = case_when(
+      num_claims == "p0" ~ "Probability of 0 Claims",
+      num_claims == "p1" ~ "Probability of 1 Claim",
+      num_claims == "p2" ~ "Probability of 2 Claims",
+      num_claims == "p3" ~ "Probability of 3 Claims"
+    )
+  ) %>%
+  ggplot() +
+  aes(x = prediction, fill = num_claims) +
+  geom_density(color = NA) +
+  facet_wrap(~num_claims) +
+  theme_classic() +
+  ylab("Probability Density") +
+  xlab("Predicted Probability") +
+  ggtitle("Distribution of Frequency Model Predictions") +
+  theme(
+    text = element_text(family = "Times New Roman"),
+    plot.title = element_text(hjust = 0.5),
+    legend.position = "none"
+  ) +
+  scale_fill_manual(values = c("#A54657", "#849698", "#0D3B66", "#EE964B"))
+  
+sev_preds %>%
+  set_colnames("prediction") %>%
+  mutate(prediction = exp(prediction)) %>%
+  ggplot() +
+  aes(x = prediction) +
+  geom_density(
+    color = NA,
+    fill = "#0D3B66"
+  ) +
+  theme_classic() +
[…]

### 2021-05-19 R/summary_plot.R
Bug in summary plot that was causing test to fail

@@ -152,6 +152,7 @@ summary_plot <- function(
   }
   
   variable_values <- variable_values %>%
+    magrittr::set_colnames(names) %>%
     dplyr::select(dplyr::all_of(important_vars)) %>%
     dplyr::mutate(
       dplyr::across(

### 2021-05-19 R/helpers-where.R
updated documentation

@@ -8,9 +8,6 @@
 #'
 #' @section Examples:
 #'
-#' ```{r, child = "man/rmd/setup.Rmd"}
-#' ```
-#'
 #' Selection helpers can be used in functions like `dplyr::select()`
 #' or `tidyr::pivot_longer()`. Let's first attach the tidyverse:
 #'
@@ -67,7 +64,7 @@ where <- function(fn) {
     out <- predicate(x, ...)
     
     if (!rlang::is_bool(out)) {
-      abort("`where()` must be used with functions that return `TRUE` or `FALSE`.")
+      rlang::abort("`where()` must be used with functions that return `TRUE` or `FALSE`.")
     }
     
     out

### 2021-05-19 R/observation_plot.R

@@ -272,4 +272,4 @@ observation_plot <- function(
     )
 }
 
-utils::globalVariables("where")
+

### 2021-05-19 R/helpers-where.R
slight updates to the documentation for `where()`

@@ -5,56 +5,8 @@
 #'
 #' @param fn A function that returns `TRUE` or `FALSE` (technically, a
 #'   _predicate_ function). Can also be a purrr-like formula.
-#'
-#' @section Examples:
-#'
-#' Selection helpers can be used in functions like `dplyr::select()`
-#' or `tidyr::pivot_longer()`. Let's first attach the tidyverse:
-#'
-#' ```{r, comment = "#>", collapse = TRUE}
-#' library(tidyverse)
-#'
-#' # For better printing
-#' iris <- as_tibble(iris)
-#' ```
-#'
-#' `where()` takes a function and returns all variables for which the
-#' function returns `TRUE`:
-#'
-#' ```{r, comment = "#>", collapse = TRUE}
-#' is.factor(iris[[4]])
-#'
-#' is.factor(iris[[5]])
-#'
-#' iris %>% select(where(is.factor))
-#'
-#' is.numeric(iris[[4]])
-#'
-#' is.numeric(iris[[5]])
-#'
-#' iris %>% select(where(is.numeric))
-#' ```
-#'
-#'
-#' ## The formula shorthand
-#'
-#' You can use purrr-like formulas as a shortcut for creating a
-#' function on the spot. These expressions are equivalent:
-#'
-#' ```{r, comment = "#>", collapse = TRUE}
-#' iris %>% select(where(is.numeric))
-#'
-#' iris %>% select(where(function(x) is.numeric(x)))
-#'
-#' iris %>% select(where(~ is.numeric(.x)))
-#' ```
-#'
-#' The shorthand is useful for adding logic inline. Here we select all
-#' numeric variables whose mean is greater than 3.5:
-#'
-#' ```{r, comment = "#>", collapse = TRUE}
-#' iris %>% select(where(~ is.numeric(.x) && mean(.x) > 3.5))
-#' ```
+#'   
+#' @return A selection of columns
 #'
 #' @name where
 where <- function(fn) {

### 2021-05-20 R/mshap.R
fixed bug in mshap function, updated paper code

@@ -130,7 +130,7 @@ mshap <- function(
     
     l <- purrr::map2(
       .x = main,
-      .y = ex_1,
+      .y = main_ex,
       .f = ~{
         multiply_shap(
           shap_1 = .x,

### 2021-05-20 inst/paper/04a_visualize_final_model.R

@@ -32,6 +32,36 @@ freq_preds %>%
     names_to = "num_claims",
     values_to = "prediction"
   ) %>%
+  filter(num_claims %in% c("p0", "p1")) %>%
+  mutate(
+    num_claims = case_when(
+      num_claims == "p0" ~ "Probability of 0 Claims",
+      num_claims == "p1" ~ "Probability of 1 Claim",
+      num_claims == "p2" ~ "Probability of 1+ Claims",
+      num_claims == "p3" ~ "Probability of 1+ Claims"
+    )
+  ) %>%
+  ggplot() +
+  aes(x = prediction, fill = num_claims) +
+  geom_density(color = NA) +
+  facet_wrap(~num_claims) +
+  theme_classic() +
+  ylab("Probability Density") +
+  xlab("Predicted Probability") +
+  ggtitle("Distribution of Frequency Model Predictions (0 and 1)") +
+  theme(
+    text = element_text(family = "Times New Roman"),
+    plot.title = element_text(hjust = 0.5),
+    legend.position = "none"
+  ) +
+  scale_fill_manual(values = c("#A54657", "#849698"))
+freq_preds %>%
+  pivot_longer(
+    cols = everything(),
+    names_to = "num_claims",
+    values_to = "prediction"
+  ) %>%
+  filter(num_claims %in% c("p2", "p3")) %>%
   mutate(
     num_claims = case_when(
       num_claims == "p0" ~ "Probability of 0 Claims",
@@ -47,17 +77,18 @@ freq_preds %>%
   theme_classic() +
   ylab("Probability Density") +
   xlab("Predicted Probability") +
-  ggtitle("Distribution of Frequency Model Predictions") +
+  ggtitle("Distribution of Frequency Model Predictions (2 and 3)") +
   theme(
     text = element_text(family = "Times New Roman"),
     plot.title = element_text(hjust = 0.5),
     legend.position = "none"
   ) +
-  scale_fill_manual(values = c("#A54657", "#849698", "#0D3B66", "#EE964B"))
-  
+  scale_fill_manual(values = c("#0D3B66", "#EE964B"))
+
+
+
 sev_preds %>%
   set_colnames("prediction") %>%
-  mutate(prediction = exp(prediction)) %>%
   ggplot() +
   aes(x = prediction) +
   geom_density(
@@ -86,10 +117,48 @@ sev_shap <- read_csv(str_c(dat_dir, "pd_sev_shap_values_final_mod.csv")) %>%
   select(-X1) %>%
[…]

### 2021-06-15 README.Rmd
added some files with my paper and talk, prepped for publishing to CRAN

--- 2021-04-19 README.Rmd
@@
 [![Travis build status](https://travis-ci.com/srmatth/mshap.svg?branch=main)](https://travis-ci.com/srmatth/mshap)
+[![Codecov test coverage](https://codecov.io/gh/srmatth/mshap/branch/main/graph/badge.svg)](https://codecov.io/gh/srmatth/mshap?branch=main)
 <!-- badges: end -->

### 2021-06-15 inst/paper/00c_functions_test_kernel.R

@@ -159,3 +159,92 @@ test_kernel_shap <- function(
     dplyr::mutate(n_var = n_var, y1 = y1,theta1 = theta1, theta2 = theta2, sample = sample) %>%
     dplyr::select(n_var, y1, theta1, theta2, sample, variable, dplyr::everything())
 }
+
+test_mshap <- function(
+  y1 = "rowSums(X)", 
+  y2 = "rowSums(X)",
+  sample = 100L, 
+  theta1 = 0.8, 
+  theta2 = 7,
+  n_var = 10
+) {
+  usethis::ui_info("Comupting performance of multiplcative SHAP for {y1} with theta1 = {theta1} and theta2 = {theta2} on {sample} samples")
+  l <- py_shap_vals_general(y1, y2, sample = sample, n_var = n_var)
+  
+  mshap_l <- mshap(
+    shap_1 = l$shap1,
+    shap_2 = l$shap2,
+    ex_1 = l$ex1,
+    ex_2 = l$ex2
+  )
+  
+  res_unif <- compare_shap_vals(
+    mshap_l$shap_vals %>% 
+      mutate(
+        expected_value = mshap_l$expected_value
+      ) %>%
+      mutate(predicted_val = rowSums(.)), 
+    l$real_shap, theta1, theta2
+  )
+  
+  res_unif$summarized %>%
+    dplyr::mutate(n_var = n_var, y1 = y1,theta1 = theta1, theta2 = theta2, sample = sample) %>%
+    dplyr::select(n_var, y1, theta1, theta2, sample, variable, dplyr::everything())
+}
+
+py_shap_vals_general <- function(
+  y1 = "rowSums(X)", 
+  y2 = "rowSums(2*X)", 
+  n_var = 50L,
+  sample = 100L, 
+  seed = 15L
+) {
+  np <- reticulate::import("numpy")
+  pd <- reticulate::import("pandas")
+  shap <- reticulate::import("shap")
+  sklearn <- reticulate::import("sklearn.ensemble")
+  gbr <- sklearn$GradientBoostingRegressor
+  
+  
+  np$random$seed(seed)
+  X <- purrr::map_dfc(.x = 1:n_var, .f = ~np$random$uniform(low = -1L, high = 1L, size = sample)) %>%
+    magrittr::set_colnames(str_c("x", 1:n_var))
+  
[…]

### 2021-06-15 inst/paper/01c_simulation_test_kernel.R

@@ -1,4 +1,4 @@
-source("mSHAP/00c_functions_test_kernel.R")
+source("inst/paper/00c_functions_test_kernel.R")
 
 # Load Libraries
 library(tictoc)
@@ -12,16 +12,16 @@ library(stringr)
 # Create a data frame of values to map across
 eqns <- list(
   y1 = c(
-    "rowSums(X)",
-    "rowMeans(X^2)",
-    "rowSums(X^2)",
-    "rowSums(2*X - X^2)",
-    "rowMeans(exp(X))",
-    "0.25 * rowSums((exp(X) / (X^2)))"
+    "rowSums(X) * rowMeans(X^2)",
+    "rowMeans(X^2) * rowSums(X^2)",
+    "rowSums(X^2) * rowSums(2*X - X^2)",
+    "rowSums(2*X - X^2) * rowMeans(exp(X))",
+    "rowMeans(exp(X)) * rowSums((exp(X) / (X^2))) * 0.25",
+    "0.25 * rowSums((exp(X) / (X^2))) * rowSums(X)"
   ),
   theta1 = c(3),
   theta2 = c(10),
-  n_var = c(10, 20, 30, 40, 50)
+  n_var = c(3, 5, 10, 20, 30, 40, 50)
 ) %>%
   expand.grid(stringsAsFactors = FALSE)
 
@@ -35,69 +35,12 @@ all_tests <- purrr::pmap_dfr(
 toc() # 4989.2 seconds (~1.4 hours)
 
 # Write data to file, include code to read it back in again
-readr::write_csv(all_tests, "mSHAP/all_tests_results_kernel_comp.csv")
-all_tests <- readr::read_csv("mSHAP/all_tests_results_kernel_comp.csv")
+readr::write_csv(all_tests, "inst/paper/all_tests_results_kernel_comp.csv")
 
-#### Distribute Alpha Winner ----
 
-all_tests %>%
-  summarise(mean_score = mean(score)) %>%
-  ungroup() %>%
-  arrange(desc(mean_score)) # weighted_abs is the best for the score
+all_tests <- readr::read_csv("inst/paper/all_tests_results_kernel_comp.csv")
 
-all_tests %>%
-  summarise(mean_dir_con = mean(direction_contrib)) %>%
-  ungroup() %>%
-  arrange(desc(mean_dir_con)) # weighted abs is the best for the direction
-
-all_tests %>%
-  summarise(mean_rel_val_con = mean(relative_mag_contrib)) %>%
-  ungroup() %>%
[…]

### 2021-06-15 inst/paper/01d_simulation_test_kernel_main.R

@@ -36,7 +36,7 @@ toc() # 4989.2 seconds (~1.4 hours)
 
 # Write data to file, include code to read it back in again
 readr::write_csv(all_tests, "mSHAP/all_tests_results_kernel_comp_main_2_eqn.csv")
-all_tests <- readr::read_csv("mSHAP/all_tests_results_kernel_comp_main_2_eqn.csv")
+all_tests <- readr::read_csv("inst/paper/all_tests_results_kernel_comp_main_2_eqn.csv")
 
 #### Distribute Alpha Winner ----
 

### 2021-06-15 inst/paper/02_paper_plots.R

@@ -74,7 +74,7 @@ all_tests %>%
   )
 
 ## Tiing Plots ----
-all_times_2_vars <- readr::read_csv("mSHAP/all_times_2_vars.csv")
+all_times_2_vars <- readr::read_csv("inst/paper/all_times_2_vars.csv")
 
 all_times_2_vars %>%
   tidyr::pivot_longer(
@@ -82,28 +82,29 @@ all_times_2_vars %>%
     names_to = "method",
     values_to = "time"
   ) %>%
-  mutate(method = ifelse(method == "kernel_time", "KernelSHAP", "Multiplicative TreeSHAP")) %>%
+  mutate(method = ifelse(method == "kernel_time", "KernelSHAP", "mSHAP")) %>%
   ggplot() +
   aes(x = smaple_size, y = time, color = method) +
-  geom_line(lwd = 1) +
+  geom_line(lwd = 1.5) +
   theme_classic() +
-  scale_color_manual(values = c("#440154", "#29AF7F")) +
+  scale_color_manual(values = c("#A54657", "#0D3B66")) +
   xlab("Sample Size") +
   ylab("Time (seconds)") +
   ggtitle("Comparison of Time by Method", "Number of Variables Fixed at 2") +
   labs(color = "Method") +
+  guides(color = guide_legend(nrow = 1, title.hjust = 0.5, title.position = "top")) +
   theme(
     legend.position = c(0.7, 0.3),
-    legend.box.background = element_rect(color = "#99A88C"),
-    plot.title = element_text(hjust = 0.5, vjust = 0.5, size = 20),
-    plot.subtitle = element_text(hjust = 0.5, size = 18),
-    axis.text = element_text(size = 14),
-    axis.title = element_text(size = 16),
-    legend.text = element_text(size = 14),
-    legend.title = element_text(size = 16)
+    legend.background = element_rect(color = "black"),
+    plot.title = element_text(hjust = 0.5, vjust = 0.5, size = 20, family = "Times New Roman"),
+    plot.subtitle = element_text(hjust = 0.5, size = 18, family = "Times New Roman"),
+    axis.text = element_text(size = 14, family = "Times New Roman"),
+    axis.title = element_text(size = 16, family = "Times New Roman"),
+    legend.text = element_text(size = 14, family = "Times New Roman"),
+    legend.title = element_text(size = 16, family = "Times New Roman")
   )
 
-all_times_100_sample <- readr::read_csv("mSHAP/all_times_100_sample.csv")
[…]

### 2021-06-15 README.Rmd
updated the README with the code coverage badge

--- 2021-04-24 README.Rmd
@@
 <!-- badges: start -->
-[![Travis build status](https://travis-ci.com/srmatth/mshap.svg?token=zA4xhwrbzL7YLqiktuAB&branch=main)](https://travis-ci.com/srmatth/mshap)
+[![Travis build status](https://travis-ci.com/srmatth/mshap.svg?branch=main)](https://travis-ci.com/srmatth/mshap)
+[![codecov](https://codecov.io/gh/srmatth/mshap/branch/main/graph/badge.svg?token=80MEJIXXX9)](https://codecov.io/gh/srmatth/mshap)
 <!-- badges: end -->

### 2021-06-15 R/mshap.R
minor spelling errors that were fixed

@@ -31,7 +31,7 @@
 #'   `shap_*_names` argument, which will still be a single character vector.
 #'
 #' @return A list containing the multiplied SHAP values and the expected value.
-#'   Or, in the case of a list passed as one of the `shap_*` aguments, a list 
+#'   Or, in the case of a list passed as one of the `shap_*` augments, a list 
 #'   of lists where each element corresponds to the same element in the list
 #'   passed to `shap_*`.
 #' @export

### 2021-06-17 README.Rmd
changes for re-submission to CRAN

@@
 
-## Attribution
+## Citations
 
 - For more information about SHAP values in general, you can visit the [SHAP github page](https://github.com/slundberg/shap)
-- If you use `{mshap}`, please cite [this article](https://www.google.com/)
+- If you use `{mshap}`, please cite [*mSHAP: SHAP Values for Two-Part Models*](https://arxiv.org/abs/2106.08990)

### 2021-06-17 R/mshap.R

@@ -36,6 +36,8 @@
 #'   passed to `shap_*`.
 #' @export
 #' 
+#' @importFrom magrittr %>%
+#' 
 #' @examples 
 #' 
 #' if (interactive()) {
